Transforming Trash as an Artistic Act

### 2015-12-06 chapter2_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

%
%
In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash (Rubbish Theory) are discussed. Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with help of ideas of philosophers (Zizek). Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash. Further it is mentioned how artist are approached these notions? and how their work viewed as their offered window or framework.

%
%
\section{Throw away culture}
[What is questioned in this section?] Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?

%
%
[Disposable items.] \comment{Disposable: made to be used once or only a few times. Made to be thrown away after one use or several uses. Not permanent or durable. Not designed to reuse again and again. For examples packages of bevarages, paper cups etc. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. I have never seen such person that uses own paper cup again and again. However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time. Importantly the term throw away society has a slightly negative connotation, or meaning. When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval. \todo{ref.}}

@@

[Factors.] \comment{Not only one factor, technological advacements can be one of them. These items with the help of industrialization can be produced easily. Mass production. Disposable items are reduces the labour and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup). Another point is that they are more affordable in terms of supply chain and cost. In other words you can put new one easily. Therefore there is no need to save the old one. Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly.} \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref. ontology of trash}

@@

[Art] There are some artists whose works are related with the pheomena expressed above. (Some of the works of artist can be examined in this pheomena.)

@@

Not every people throw away disposible objects, some of them save them and use for their own purposes.

@@

%
%
\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of peoples life. What people consume is actually tells many things about them \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}. As scholars mentioned that throughout the discards of someone else many thing can be understand. They are end product of our activities and it can be traced through the discard and garbage.

%
%
[GARBOLOGY] Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.

@@

\todo{transition needed.} With the help above understanding of trash, what can we see the work of arts. For examples tracey emin.

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. It is a time capsule. The cigarettes that litter the floor will one day no longer exist; neither will the newspapers. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo{Hastalık dönemi... Sanattaki yerine bakmak gerekli.}

%
%
\section{Zizek's Approach to Rubbish}
[Transition, introduction] 
\todo{Adam bir transition bulmalı buraya.} Last decades increasing attention the the ecology and rubbish. This section is related with the increasing interest on ecology. Global warming is one of them, plastic pollution on the oceans also is part of it. These types of news and talks increasingly find a place on media more and more. Zizek comments on ecology and trash.

In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London. His part starts with these sentence: \quote{This [garbage dump] is where we should start feeling at home}.

@@

Transforming trash is not related with ecological perspective. We are not trying to save the planet earth or mother nature. Beyond ecological concerns we are trying to find ways to live our trash.

@@

>>>>

%
%
In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash (Rubbish Theory) are discussed. Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with the help of ideas of philosophers (Zizek). Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash. Further it is mentioned how artist are approached these notions? and how their work viewed as their offered window or framework.

%
%
\section{Throw away culture}
Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?

%
%
\comment{[Disposable items.]}
\comment{Disposable: made to be used once or only a few times. Made to be thrown away after one use or several uses. Not permanent or durable. Not designed to reuse again and again. For examples packages of bevarages, paper cups etc. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. I have never seen such person that uses own paper cup again and again. However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time. Importantly the term throw away society has a slightly negative connotation, or meaning. When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval. \todo{ref.}}

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\comment{LIFE AN OBJECT} \paraphrase{In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of. This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste. In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\comment{REFLOW IN THE MARKET} \paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new. The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

\comment{[Capitalism, market.]} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap. They were designed to decrease in value over time - to be used one, or twice and than to be thrown away. This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products. themselves. \todo{Waste and wantta bununla ilgili bir bölüm olmalı.}

\comment{[Initial function.]} 
When an object is discarded it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown out as trash.

@@

\comment{CONSUMER CULTURE}
\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these thesis are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century. In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}

%
%
\comment{[Factors.]}
Factors that cause over consumption habits. Technological advacements can be one of them. These items with the help of industrialization can be produced easily. Mass production. Disposable items are reduces the labour and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup). Another point is that they are more affordable in terms of supply chain and cost. In other words you can put new one easily. Therefore there is no need to save the old one. Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref. ontology of trash}

@@

%
%
[Art] There are some artists whose works are related with the pheomena expressed above. (Some of the works of artist can be examined in this pheomena.) Not every people throw away disposible objects, some of them save them and use for their own purposes.

@@

@@

%
%
\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of people's life. What people consume is actually tells many things about them (their choices, possessions etc.) \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}. As scholars mentioned that throughout the discards of someone else many thing can be understand. They are end product of our activities and it can be traced through the discard and garbage.

% TODO need relocation
% FROM Culture, Values, and Garbage, Encyclopedia 
%\comment{INTERACTION WITH GARBAGE. VALUE SYSTEM, DECIDING TO GARBAGE.}
%\paraphrase{"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share. In terms of their relationship to garbage, all people interact with it on two levels. One is a material connection, indicative of the physical and sensory contacts that people have with garbage. In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends. Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside. The second connection that people maintain with garbage is an ideational one. Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition. The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object. Instead, humans determine whether the object is of value or whether it is considered trash. The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package. The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}}

% TODO need relocation.
% FROM Garbage in Modern Thought, Encyclopedia
%\comment{THROW AWAY CULTURE.} 
%\paraphrase{Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.” "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash. It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions. Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}

% TODO need relocation.
% FROM Garbage in Modern Thought, Encyclopedia
%\comment{CATEGORIZATION.} \paraphrase{"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay. Consumers have become accustomed to the categories that are often applied to garbage. Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper). Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}}

% TODO need relocation.
% Garbage is universal.
%\comment{NO VALUE, UNIVERSAL} \paraphrase{"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted. Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value. While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined. Many non-Western societies attach a much greater value to items after they are discarded. In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value. Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture. People define what is trash and what is valuable." \cite{lukas2012garbage}}

\todo[inline] transition required.

%
%
\comment{[GARBOLOGY]}
Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.

@@

\todo{transition required.} With the help above understanding of trash, what can we see the work of arts?

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo{Hastalık dönemi... Sanattaki yerine bakmak gerekli.}

%
%
\section{Zizek's Approach to Rubbish}
\todo[inline]{transition required.} 
Last decades increasing attention the the ecology and rubbish. This section is related with the increasing interest on ecology. Global warming is one of them, plastic pollution on the oceans also is part of it. These types of news and talks increasingly find a place on media more and more. At this stage Zizek comments on ecology and trash conversly .

% TODO new comer
% \paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}

In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London. His part starts with these sentence: \quotes{This [garbage dump] is where we should start feeling at home}.

@@

Transforming trash is not related with ecological perspective. We are not trying to save the planet earth. Beyond ecological concerns we are trying to find ways to live our trash.

@@

% Rubbish theory'de durable dediğimiz bir kategori var. mesela picassonun sözü de buna bir şekilde karşı duruş sergiliyor. Çünkü dönüştürmenin devamlılığını arzuluyor. Ama durable olan şeyin bir konumu sabitlenmiş oluyor herhalde.

% TODO new comer.
%\comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control. As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous. The socially constructed value of the object has shifted over time from its finite life span of usefulness and meaning to a timeless and valueless of socially sanctioned rubbish.

% TODO new comer
\comment{MOVES.} \paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed. (Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{ref.}

% TODO new comer
\comment{MOVES.} \paraphrase{Objects moves around and their values change constantly. (The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.). The Social Life of Things: Commodities in Cultural Perspective)}\todo{ref.}

% TODO new comer
% BAZI KISIMLARINI AÇMAK GEREKLİ AMA.
\comment{MOVES.} Here the important thing is moving nature of trash. Objects moves and gains different meanings through this movement. Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle. It also signifies that it is relative and result of a classification issue.

% TODO new comer
% From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
\comment{MOVES.} \paraphrase{Below part explains journey of trash in different steps/stages. Object moves and trash also moves. How is it life of trash? This part explains life of trash. How does it intersect with other people in which places? This part also can be understand by pointing out different part of it with detailed explanation. For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill. In other words there are different places to touch on trash. Every place generates different story? Or to understand it more deeply it covers different part of it. Or provides ideas about it. Lots of people touches it from philosophers to artist. Also in the later parts it draws attention to them.}

% TODO new comer
% Ama çöp olarak zaten kalmıyor. Bir şekilde hayatımıza tekrar giriyor. Ne kadar itise de... Trashion: the return of disposed. Peki geri dönüşü nasıl bir değişiklik yaratıyor. Ya da gerçekten geri geliyor mu? Kullandığımız ürünlerin ne kadarı tek kullanımlık. Tek kullanımlıklarla nerede karşılaşıyoruz. Evet belki hayatımızda çok kullanılan şeyler var fakat. Daha tek kullanımlıklar da var denilebilir.
\comment{TRASH MOVES.} \paraphrase{Trash moves, all the time. It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill. Even in the landfill, it does not remain still. Monster "waste handling dozers" move rubbish around, compact it and press it against the soil. More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche. When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement. This is how trash moves. But\ldots who moves on trash? In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish. In Latin America, it is mostly people. People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks. In many of the garbage dumps around the world, scavenging becomes a steady job. \quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is. (through the works of Filomena Cruz's photographic series “Road Kill”)}

% TODO new comer
\comment{CATEGORIZATION OF WASTE} \paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are. (Think that the transformation process. Previous argument support that the transformation of trash is possible by changing the place of them. In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’. For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.} \todo{Reference, (Waste by William Viney).}

% TODO new comer
\comment{CATEGORIZATION OF WASTE} \paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position. Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}

% TODO new comer
\comment{CATEGORIZATION OF WASTE} \comment{susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte. Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda. Remember the example given: shoes  on the dinner table.}

\comment{CATEGORIZATION OF WASTE} \paraphrase{waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}

\quotes{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}

### 2015-12-06 chapter3_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

@@

@@

@@

@@

@@

@@

%
% Sample phrases
% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently. Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing. With recycled objects, one can build anti-seismic and energy efficient houses. Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters. There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use. Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio. Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules. David Hertz reused the wings of a 747 as roof for a villa in Malibu. TYIN Tegnestue architects restored a building with recycled materials, mainly found on location. Yatin Pandya and Footprints E.A.R.T.H. built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners. James & Mau and Infiniski designed fashion homes with recycled containers. The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion. The GAD. In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials. The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling. All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.

>>>>

% Bicycle wheel duchamp 1913.

@@

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{hybrid} each recycled object contains within it a reference to two or more distinct times. \comment{not every time actually, if you transfor ok. it applicable for my case.} Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992) \todo{ref.}

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{HYBRIDITY} \paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another. Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world. It is story of people --- the women, men, children etc. one person's trash into another's treasure.}

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{HYBRIDITY} They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{SEMIOTIC CONTEXT} \quotes{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence. Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others. (Jacknis 1992)} \todo{ref.}

% TODO new comer
\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}

@@

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors). From western trash to tribal treasure. \paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods. A disposable item becomes imminent desire and profound social consequence. (Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function. It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\todo{yerlinin fotoğrafı}
\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head. In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}

%(Summary From Paul M Camic.) 
The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder. It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes. The junk object becomes transformed into the valued found object. Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965). His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p. 97) and labeled it a work of art. A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996). These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.

Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p. 169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p. 170). The finder discovers an unrealised significance in the object. A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object. He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context. \ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).

How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination. (Important points a gap in the literature. Although Parsons article analyze practices, it is not very broad and detailed. Further what is the importance of it is missing.)

The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident. The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.

Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater. The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements. When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object. Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder. This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.

An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time. Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.

Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.

% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century. To help contextualize the application of found objects, the following section provides an overview of their use by Western artists. This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.

% Amelie olabilir. Orada fotoğraf toplayan çocuk olabilir. Onları itinayla toplayan bir adam. Tren garındaki fotoğraf kulubesi. Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası. Bir birinden farklı bir sürü insan. Filmde neden böyle bir eyleme yer veriliyor? Film fotoğraflar üzerinden defter üzerinden ilerliyor. Onun çevresinden bir hikaye kurgulanıyor. İnsanların artıklarını topluyor. Onların değer vermedikleri şeyleri topluyor. Bunlar baya baya aslında o insanlar. Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor. Çok iyi bir örnek mi bilmiyorum. Burada niyet nedir ki? Ben buna şöyle bir okuma getireceğim diyebilirim. Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde. Bu arada bu fotoğraf toplama işi ilk değil. Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte. Ama benim işime yarayan kısmı ne? Neden o fotoğrafları ya da bunun filmini yapıyor. Aslında puzzlelar üretiyor. Belirli tekrar olacaktır. insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir. Tekrar bir kitap haline geliyor. Tanınmayan insanların fotoğrafları. Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon. Aslında tam da amelie bunu yapmıyor mu? Hikayeler üretiyor bu fotoğraflardan. Yeni karşılaşmalar üretmesi. Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır. Bin bir türlü şey vardır aralarında. Nereye yerleşmeli. Başkasının çöpünü toplama. O dönemin o eşyasını arşivini tutma. ve herkes sunuluyor sonrasında bu.

@@

% not easily understandable with the entering non-art objects in art. artist are responding the current societies habits in a different ways. what they are doing here is to see other possibliteis and show actually what is going on. what does it mean all of these things.

@@

% TODO new comer.
[indigenization] the indigenization of western objects. (sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"? Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves. They do not necessarily despise our commodities. But they are selective in their demands and transformative of their uses of such things. (sahlins, 13)"

\comment{This is a proff of the transformation of the original concept.}

% TODO new comer.
[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse. but even if they have no economical struggle, they continue recycle. what is the reason of it?} Recycling as an economic strategy of survival in developing countries throughout the world. creative production that is motivated, primarily, by adverse conditions of economic necessity. (lanfill orchestra here. bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised. (p25)

@@

[Chrish Jordan Break Down inventory] \paraphrase{Not all artist transform trash although some deconstruct them. Michael Landy is one of them. Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections.} It can be an example of downcycling process. It is preferred to decompose all the complex link and relationships between the objects. They are not just ordinary things they are possessions of artist. Break Down 2001, in which he systematically destroyed all his personal possessions. His work examines what we value and what we discard, consumerism and waste, and human labour and its worth. It happens in public space. People can see the process. This process last 2 weeks. Places where people buy things actually.

%\comment{Tüm sahip olduklarını yaşarken kendi isteği ile yok ediyor. Bu hepimizin paylaştığı bir şey.}

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
  \caption{Chris Jordan, Break Down}
  \label{fig:ChrisJordan_BreakDown}
\end{figure}

@@

% TODO new comer
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
[Resistance] \comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence. (sahlins 1992, 16)"

% TODO new comer
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
[Ironic] \comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic. the irony is often embodied visually and conceptually. opposite of natural use, expected perception. for example making something from nothing or turning trash into treasure. By juxtaposing different materials changing context and place.

% TODO new comer
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people. It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."

% Günlük rutinleri çöp üzerinden yakalayanlar var. Her gün ürettiği çöpün fotoğrafını çeken insan... Ürettikleri çöpleri ifade etme araçları olarak kullananlar.
